A generalized definition of multidimensional item response theory parameters

### 2023-03-03 output/paper_draft/paper_M2PLM_parameters.Rmd
Adds again Mario's changes to section "Test space and latent space"

Before defining the multidimensional parameters, we need to make a clarification
regarding the representation of the items in the latent space.
Equation \@ref(eq:slope-param) makes it clear that a space $`r TEST_SPACE`$
with basis $`r ITEM_SPACE_BASIS_EQ`$ and inner product matrix
$`r INNER_PROD_MATRIX_INV`$ can be defined,
such that $`r INNER_PROD_DISCR_EQ`$ and, subsequently,
$`r DISCR_VECTOR_MODULE_EQ`$.
We call $`r TEST_SPACE`$ the *test space* [@zhang_theoretical_1999] of the
discrimination vectors.
This space is where the item vectors can be properly represented.
It is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces,
as their inner product matrices are inverse of one another.

With this definition we have that

@@

It is clear that $`r INNER_PROD_INV_MAT_ELEMENT_EQ`$ were
$`r INNER_PROD_INV_MAT_ELEMENT`$ is the $`r INNER_PROD_INV_MAT_SUBINDEX`$-th
element of $`r INNER_PROD_MATRIX_INV`$.

Let $`r LS_STD_BASIS`$ be the standard basis of $`r TEST_SPACE`$.
Then, $`r BASIS_CHANGE_TS_EQ`$ is the change of basis matrix and
$`r DISCR_VECTOR_STD_MOD_EQ`$.

>>>>

Before defining the multidimensional parameters, we need to make a clarification
regarding the representation of the items in the latent space.
We call $`r TEST_SPACE`$ the *test space* [@zhang_theoretical_1999] of
the discrimination vectors.
This space is where the item vectors can be properly represented.
It is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces.
Let's consider the model given by Equation \@ref(eq:M2PL-formulation),
where the latent traits and the parameters $a_i$ are expressed in the same basis
$`r LS_BASIS`$ in their respective spaces.

Since the response probability must be invariant, because of Equation
\@ref(eq:change-basis), parameter $`r DISCR_VECTOR`$ must also be transformed
in $`r DISCR_VECTOR_STD`$.
Equating the probabilities we get $a_1^{'}=P^{-1^T}a_i=M^{-1}Pa_i$ .
This shows that first a basis change to the standard base is performed and then
a transformation through $`r INNER_PROD_MATRIX_INV`$,
so the $`r DISCR_VECTOR_STD`$ are expressed in the standard basis.

\begin{equation}
  `r DISCR_VECTOR_MODULE_EQ`                     (\#eq:discr-param-squared-norm)
\end{equation}

Therefore, in the test space, an inner product matrix
$`r INNER_PROD_MATRIX_INV`$ can be defined such that $`r INNER_PROD_DISCR_EQ`$,
to keep the norm invariant.
With this definition we have that

@@
